Analysis for Performing-Articulation performances (ONSET)

### 2020-05-19 material/analysis/expression/stim_a/ioi_onset.Rmd
update layout
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Analysis for Non-Expressive performances (ONSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance from teaching-v2.0 (onsets).

@@

### Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```

# IOI Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[, .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

>>>>

---
title: 'Analysis for Performing-Articulation performances (ONSET)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of performing performance (IOI-Onset) from teaching-v2.0.

@@

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r ioi_all$N-nrow(excluded_ioi)`

# IOI Variability
## 1. All - individual
- Average CV for each participant

```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[, .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```
